### 2021-04-12 Chapter-5/Chapter-5.tex
Updates from Overleaf

According to Chi Square Distribution Table, we have the probability $p=0.95$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (a). We have the probability $p=0.00$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (b).
\section{Design}
In this section, we explain the implementation of \ctool{}.
we first present the overview of \ctool{}. After that, we discuss some design details to implement \ctool{}.

>>>>

According to Chi Square Distribution Table, we have the probability $p\approx0.95$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (a). We have the probability $p\approx0.00$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (b).
\section{Design}
In this section, we explain the implementation of \ctool{}.
we first present the overview of \ctool{}. After that, we discuss some design details to implement \ctool{}.
